%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.365\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Rahul}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Arasikere}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Software Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.335\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Linkedin}{12}{\href{https://linkedin.com/in/rahul-arasikere}{linkedin.com/in/rahul-arasikere}}\\
	\icon{Phone}{12}{+91 9901191056}\\
	\icon{At}{12}{\href{mailto:arasikere.rahul@gmail.com}{arasikere.rahul@gmail.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.3\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{12}{\href{https://rahul-arasikere.github.io/?ref=resume}{rahul-arasikere.github.io}}\\
	\icon{Github}{12}{\href{https://github.com/rahul-arasikere}{github.com/rahul-arasikere}}\\
	\icon{Twitter}{12}{\href{https://twitter.com/@rahul_arasikere}{@rahul\_arasikere}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{9/2018 -- 5/2022\\\footnotesize{ongoing}}
		{Bachelor's Degree in Computer Science}
		{Boston University}
		{CGPA: 3.0/4.0.}
	\entry
		{2018}
		{CBSE 12th}
		{Sindhi High School Hebbal}
		{93\%.}
	\entry
		{2016}
		{ICSE 10th}
		{Vidya Niketan School}
		{87\%.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{6/2019 -- 8/2019}
		{Data Science Intern}
		{Remidio Innovative Solutions Pvt. Ltd.}
		{Developed an automated pipeline for detection of age-related macular 
		degeneration in fundus images captured from Remidio’s telematic platform. Model 
		achieved 82\% accuracy over 3200 images of various qualities.\\ \texttt{Python}
		\slashsep\texttt{Keras}\slashsep\texttt{Pytorch}}
	\entry
		{6/2018 -- 7/2018}
		{Intern}
		{Spectral Insights}
		{Worked with a team of 2 – 3 people in implement AI on top of digital images of 
		renal biopsies to automatically detect glomeruli and display it on the screen to
		the doctor. Gained technical insight and experience as to how professional 
		companies’ function. \\ \texttt{C++}\slashsep\texttt{OpenCV}
		\slashsep\texttt{Linux}}
	\entry
		{5/2018 -- 6/2018\\\footnotesize{freelance}}
		{Web Developer}
		{Mansha Vacuum Technologies Pvt. Ltd.}
		{Revamped the current corporate website and migrated it to WordPress. Learned 
		SEO and making a website more visible on search engines. \\ \texttt{PHP}
		\slashsep\texttt{WordPress}\slashsep\texttt{MySQL}\slashsep\texttt{SEO}}
	\entry
		{7/2016 -- 10/2016\\\footnotesize{freelance}}
		{Web Developer}
		{The Rejuvenators}
		{Developed the first version of their website. Customized html templates and 
		plugins for WordPress. \\ \texttt{PHP}\slashsep\texttt{WordPress}\slashsep
		\texttt{MySQL}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
	\entry
		{1/2020 -- 5/2020}
		{Software Developer}
		{BU SPARK!}
		{Worked with a team of 7, to develop a chrome extension Bookworm as our official submission to the spark fellowship program.
		We won best overall idea and generated interest towards developing as a fully fledged app.\\
		\texttt{JavaScript}\slashsep\texttt{React}\slashsep\texttt{Firebase}}
	\entry
		{9/2018 -- Present}
		{Software Developer}
		{Boston University Rocket Propulsion Group}
		{Lead and developed a concurrent socket based data acquisition software for custom test stands.
		Developing RTOS based flight computer firmware for sub-orbital launch vehicle. Worked 
		on telemetry modules using LoRa. \\\texttt{Arduino}\slashsep\texttt{C}\slashsep\texttt{Python}
		\slashsep\texttt{FreeRTOS}}
	\entry
		{1/2019 -- 5/2019}
		{Junior Analyst}
		{Boston University Finance Club}
		{Worked within a team of 5 people to analyze and recommend various stocks to the investment committee.}
		
\end{entrylist}
%----------------------------------------------------------------------------------------

\end{document}
